environmental_data_preperation

### 2018-10-22 src/environmental_data_preperation.Rmd
mass netcdf to raster bricks

# NetCDFs (Biomer and GLORYS)
read in a netcdf
note this is a GLORYS dataset
```{r}
library("ncdf4")
ncbr <- brick("../data/env/1993_01_salinity.nc")
ncbr
```

@@

library(raster)
canada_eq_ar_proj <- "+proj=aea +lat_1=50 +lat_2=70 +lat_0=40 +lon_0=- +x_0=0 +y_0=0 +ellps=GRS80 +datum=NAD83 +units=m +no_defs"
library("rgdal")
rp <- projectRaster(ncbr, crs = canada_eq_ar_proj)
rp
writeRaster(rp,'../data/env/rp.tif',options=c('TFW=YES'))

>>>>

# NetCDFs (Biomer and GLORYS)
read in a netcdf
note this is a GLORYS dataset
```{r}
library("ncdf4")
testnc <-  "../data/env/1993_01_salinity.nc"
ncbr <- brick(testnc,lvar = 4) #lvar = 4 loads the levels
ncbr 
```

@@

#```{r}
library(raster)
canada_eq_ar_proj <- "+proj=aea +lat_1=50 +lat_2=70 +lat_0=40 +lon_0=-60 +x_0=0 +y_0=0 +ellps=GRS80 +datum=NAD83 +units=m +no_defs"
library("rgdal")
rp <- projectRaster (ncbr, crs = canada_eq_ar_proj)
rp
plot(rp[[1]])
writeRaster(rp[[1]],'../data/env/rplayer.tif',options=c('TFW=YES'), overwrite=TRUE) 
#```
